---
title: "All Groups Mapping"
author: "Kristin Walker"
date: "3/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages  
Load the following libraries. If they are not installed, run install.packages("packagename")
```{r results='hide', warning=FALSE, message=FALSE}
library(rmarkdown)
library(ggplot2) 
library(beeswarm)
library(MASS) 
library(generalhoslem) 
library(qwraps2) 
library(quantreg) 
library(olsrr)
library(car)
library(ggpubr)
library(dplyr)
library(tidyr)
library(lme4)
library(VGAM)
library(gridExtra)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(olsrr)
```



## Dataframes Setup
1. Import the data from a CSV file 
    + Should have *224 rows* 
```{r results='hide'}
setwd("~/Desktop/UConn Manuscripts/MappingPaper/AllGroupMapping")
Map_All <- read.csv("Mapping_Coding_KW_210309.csv", na.strings = "N/A")
dim(Map_All)
```

2. Subset data by age group (4;6-9;11)  
    + Should have *220 rows* (includes children never tested on this task)  
```{r results='hide'}
Map49 <- subset(Map_All, Map_All$Age_Rounded>=4.5 & Map_All$Age_Rounded<10 | is.na(Map_All$Age_Rounded))
dim(Map49)
```
    
3. Create a new dataframe from desired subset (e.g., children we are including in the analyses)
    + Should have *__190 rows__*
```{r results='hide'}
Map_Inc <- subset(Map49, Map49$Including.in.Study == "Yes" & Map49$Coded. == "Yes" & Map49$Mapping_Include. == "Yes" & Map49$SES != '')
dim(Map_Inc)
```
View(Map_Inc)



## Participant Demographics
* Four Participant Groups
    + EE: English Early, hearing children exposed to English from birth
    + EL: English Later, D/HH children exposed to English "later"
    + AE: ASL Early, D/HH children exposed to ASL from birth (have at least 1 D/HH parent)
    + AL: ASL Later, D/HH children exposed to ASL "later" (have hearing parents)

* How many children were tested, but were not included in analyses?   
    + 6 total: 3 had additional disabilities/suspected disabilities, 1 refused to participate, 1 due to technical difficulties (not filmed entirely), 1 Early ASL child tested in English after trying ASL (difficult to communicate with)
```{r}
Map_Not_Inc <- subset(Map49, Map49$Tested == "Yes" & Map49$Mapping_Include. == "No")
nrow(Map_Not_Inc)
```

* Does the status of including in study depend on which group children were in?  
    + No, the status of inclusion in study is not dependent on group (p > 0.05).
```{r warning=FALSE}
EE_Inc <- subset(Map_Inc, Map_Inc$Group_4cat == "English Early")
EL_Inc <- subset(Map_Inc, Map_Inc$Group_4cat == "English Later")
AE_Inc <- subset(Map_Inc, Map_Inc$Group_4cat == "ASL Early")
AL_Inc <- subset(Map_Inc, Map_Inc$Group_4cat == "ASL Later")

EE_Not_Inc <- subset(Map_Not_Inc, Map_Not_Inc$Group_4cat == "English Early")
EL_Not_Inc <- subset(Map_Not_Inc, Map_Not_Inc$Group_4cat == "English Later")
AE_Not_Inc <- subset(Map_Not_Inc, Map_Not_Inc$Group_4cat == "ASL Early")
AL_Not_Inc <- subset(Map_Not_Inc, Map_Not_Inc$Group_4cat == "ASL Later")
rnames <- c("Including in Study","Not Including in Study")
cnames <- c("English Early","English Later","ASL Early","ASL Later")
Table_IncStudy <- matrix(c(nrow(EE_Inc),nrow(EL_Inc),nrow(AE_Inc),nrow(AL_Inc),nrow(EE_Not_Inc),nrow(EL_Not_Inc),nrow(AE_Not_Inc),nrow(AL_Not_Inc)), nrow=2, ncol=4, byrow=TRUE, dimnames=list(rnames,cnames))
Table_IncStudy
chisq.test(Table_IncStudy)
```   

* Demographic table information: descriptive statistics for total children and for each group (e.g., EE, EL, AE, AL)    
```{r results='hide'}
#Recode Ethnicity to combine Unsure/Missing Categories
Map_Inc$Ethnicity <- dplyr::recode(as.character(Map_Inc$Ethnicity), 'Hispanic or Latino' = "Hispanic or Latino", 'Not Hispanic or Latino'="Not Hispanic or Latino", 'Unsure'="Unsure/Missing", 'Missing' = "Unsure/Missing", .missing="Unsure/Missing")

#Recode Race to combine Unsure/Missing Categories
Map_Inc$Race <- dplyr::recode(as.character(Map_Inc$Race), 'White' = "Caucasian", 'Black or African American'="African American", 'American Indian or Alaska Native'="American Indian or Alaska Native", 'Mixed' = "Other", 'Other' = "Other", 'Unsure' = "Unsure/Missing", 'Missing' = "Unsure/Missing", .missing="Missing")

#Reorder Grade
Map_Inc$Grade. <- factor(Map_Inc$Grade., levels=c("Pre-Kindergarten", "Kindergarten", "1st", "2nd", "3rd", "4th"))

#Reorder Ethnicity 
Map_Inc$Ethnicity <- factor(Map_Inc$Ethnicity, levels=c("Not Hispanic or Latino", "Hispanic or Latino", "Unsure/Missing"))

#Reorder Race 
Map_Inc$Race <- factor(Map_Inc$Race, levels=c("Caucasian", "Asian", "African American", "American Indian or Alaska Native", "Other", "Unsure/Missing"))

table1::label(Map_Inc$Age_Rounded) <- "Age (years)"
table1::label(Map_Inc$SES) <- "SES"
table1::label(Map_Inc$M.F) <- "Sex"
table1::label(Map_Inc$Race) <- "Race"
table1::label(Map_Inc$Ethnicity) <- "Ethnicity"
table1::label(Map_Inc$Grade.) <- "Grade"

table1::table1(~Age_Rounded + SES + M.F + Race + Ethnicity + Grade.| Group_4cat, data = Map_Inc)

#When were children tested? 
Map_Inc$SchoolYear_Timing <- factor(Map_Inc$SchoolYear_Timing, levels=c("Beginning", "Middle", "End"))
table1::label(Map_Inc$SchoolYear_Timing) <- "When Children Were Tested"
table1::table1(~SchoolYear_Timing | Group_4cat, data = Map_Inc)
```




## Analyses

> General Performance  

* Performing significantly greater than chance? 
    + Yes for overall and four pariticpant groups, all p < 0.001
```{r}
wilcox.test(Map_Inc$AvgCorrect_Total, mu = .25, alternative = "greater") 
wilcox.test(EE_Inc$AvgCorrect_Total, mu = .25, alternative = "greater")
wilcox.test(AE_Inc$AvgCorrect_Total, mu = .25, alternative = "greater") 
wilcox.test(EL_Inc$AvgCorrect_Total, mu = .25, alternative = "greater") 
wilcox.test(AL_Inc$AvgCorrect_Total, mu = .25, alternative = "greater") 

#https://github.com/emlini/SLaM-Give-N/blob/main/Carrigan_Coppola_Shusterman_GiveN_code.Rmd#L126
ggplot(data=Map_Inc, mapping = aes(x=Group_4cat, y=AvgCorrect_Total)) + geom_boxplot() + geom_dotplot(method = "dotdensity", binaxis = "y", stackdir = "center", dotsize=0.5, stackratio = 1.25) + theme(text = element_text(size=11))  + xlab("Participant Group") + ylab("Mapping Overall Proportion Correct")
```

* Performance at or near ceiling (greater than or equal to 90%)
    + 58% of children performed at or near ceiling.
```{r}
Ceil <- Map_Inc$AvgCorrect_Total
All <- .9 #ceiling performance 
Var <- length(which(Ceil>= All))
N_O <- nrow(Map_Inc) 
(Var/N_O)*100
```

> QUESTION 1: What is the relationship between language experience and mapping skills?

* [Helpful Tobit Model Link](https://stats.idre.ucla.edu/r/dae/tobit-models/)      
* Create dataframe for tobit models (includes adding set size and mapping pair columns)
    + Should have *__1710 entries / 9 =  190 children__*
    + 9 rows for each child because we have 3 set sizes for each of the 3 different mapping pairs (Numeral-Word, Quantity-Word, Quantity-Numeral)

```{r results='hide'}
which(colnames(Map_Inc)=="AvgCorrect_Med_QW") #368
which(colnames(Map_Inc)=="AvgCorrect_Lrg_WN") #373
T_long <- pivot_longer(Map_Inc, cols = 368:373, values_to = "AvgCorr")
which(colnames(T_long)=="Item1_QN_Answer") #35
which(colnames(T_long)=="Item51_WN_Correct.") #343
T_short <- T_long[,-c(35:343)]
T_short <-  mutate(T_short, SetSize = case_when(grepl("Med", T_short$name) ~"Medium", grepl("Lrg", T_short$name) ~"Large"))
T_short$SetSize <- as.factor(factor(as.character(T_short$SetSize), levels=c("Medium", "Large"), exclude=""))
T_short <- mutate(T_short, MapPair = case_when(grepl("QW", T_short$name) ~ "Quantity-Word", grepl("QN", T_short$name) ~"Quantity-Numeral", grepl("WN", T_short$name) ~"Numeral-Word"))
T_short$MapPair <- as.factor(factor(as.character(T_short$MapPair), levels=c("Numeral-Word","Quantity-Numeral", "Quantity-Word"), exclude=""))
T_short$MapPair_refQW <- as.factor(factor(as.character(T_short$MapPair), levels=c("Quantity-Word","Numeral-Word","Quantity-Numeral"), exclude=""))
```

View(T_short)


#### Tobit model #1 (ages 4;6-9;11)
* Outcome variable: Overall Mapping Performance
* Predictors: Age + SES + Modality + Timing + Set Size + Map Pair + Timing x Modality
* Result: Hauck-Donner effect for Age due to ceiling effect
```{r warning=FALSE}
summary(Map_t<- vglm(AvgCorr ~  Age_Rounded + SES + Modality + Timing + SetSize + MapPair + Timing:Modality, tobit(Upper = 1), data = T_short))
```

```{r message=FALSE, fig.align='center', fig.height=4, fig.width=5}
ggplot(data = Map_Inc, mapping = aes(x=Age_Rounded, y=AvgCorrect_Total)) + geom_point() + geom_smooth(method="loess", color="black") + labs(x="Age (years)", y="Mapping Proportion Correct Overall") + theme_bw() + theme(legend.position="top", text = element_text(size=16), panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + coord_cartesian(xlim = c(5, 10), ylim= c(0.2,1)) + scale_y_continuous(breaks=c(0.2, 0.4, 0.6, 0.8, 1)) + scale_x_continuous(breaks=c(5, 6, 7, 8, 9, 10)) + geom_hline(yintercept=0.25, linetype="dashed", color = "black")
```

#### Tobit model #2 (ages 4;6-7;11). Not including 8 to 9-year-olds to avoid Hauck-Donner effect. 
* Should have *__810 entries / 6 =  135 children__*
```{r}
Map_58 <- subset(T_short, T_short$Age_Rounded <8)
nrow(Map_58) 
```
* Outcome variable: Overall Mapping Performance
* Predictors: Age + SES + Set Size + Map Pair + Modality + Timing + Timing x Modality
* Result: All predictors besides Modality are significant

__Model 2a: Reference Group is Numeral-Word__
```{r}
summary(Map_58_I<- vglm(AvgCorr ~  Age_Rounded + SES + Modality + Timing + SetSize + MapPair + Modality:Timing, tobit(Upper = 1), data = Map_58))
```
__Model 2b: Reference Groups is Quantity-Word__
```{r}
summary(Map_58_I_ref<- vglm(AvgCorr ~  Age_Rounded + SES + Modality + Timing + SetSize + MapPair_refQW + Modality:Timing, tobit(Upper = 1), data = Map_58))
```

* Create dataframe for 4;6-7;11 year olds
    + Ensure has 135 children
```{r}
Map_Inc_58 <- subset(Map_Inc, Map_Inc$Age_Rounded <8) 
nrow(Map_Inc_58)
```

```{r results='hide'}
M <- ggplot(data=Map_Inc_58, mapping = aes(x= Modality, y=AvgCorrect_Total)) + geom_boxplot() + geom_dotplot(mapping=aes(fill=Modality, color=Modality), alpha=0.7, dotsize = .8, method = "dotdensity", binaxis = "y", stackdir = "center") + theme_bw() + theme(legend.position="top", text = element_text(size=14), axis.title.x=element_blank(), panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + ylab("Proportion Correct") + ggtitle("a") + scale_fill_manual(name = "Language Modality", breaks=c("ASL", "English"), values=c("tan2", "forestgreen"), labels=c("ASL (62)", "English (73)")) + scale_color_manual(name = "Language Modality", breaks=c("ASL", "English"), values=c("tan2", "forestgreen"), labels=c("ASL (62)", "English (73)")) + stat_summary(fun=mean, geom="point", shape=18, size=5, color="black") + geom_hline(yintercept=0.25, linetype="dashed", color = "black")
T <- ggplot(data=Map_Inc_58, mapping = aes(x= Timing, y=AvgCorrect_Total)) + geom_boxplot() + geom_dotplot(mapping=aes(fill=Timing, color=Timing), alpha=0.7, dotsize = .8, method = "dotdensity", binaxis = "y", stackdir = "center") + theme_bw() + theme(legend.position="top", text = element_text(size=14), axis.title.x=element_blank(), panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + ylab("Proportion Correct") + ggtitle("b") + scale_fill_manual(name = "Language Timing", breaks=c("Early", "Later"), values=c("deepskyblue3", "firebrick3"), labels=c("Early (64)", "Later (71)")) + scale_color_manual(name = "Language Timing", breaks=c("Early", "Later"), values=c("deepskyblue3", "firebrick3"), labels=c("Early (64)", "Later (71)")) + stat_summary(fun=mean, geom="point", shape=18, size=5, color="black") + geom_hline(yintercept=0.25, linetype="dashed", color = "black")
```

```{r message=FALSE, fig.height=4, fig.width=10}
grid.arrange(M,T,nrow=1)
```


* [Create HTML tobit model tables](https://strengejacke.github.io/sjPlot/articles/tab_model_estimates.html)
    + Will need to edit after to add R-squared values
```{r}
tab_model(Map_58_I, auto.label = FALSE, show.ci = FALSE, show.se = TRUE, show.stat = TRUE, show.est = TRUE, pred.labels = c("Intercept 1", "Intercept 2","Age", "SES", "Modality (English)", "Timing (Later)", "Large", "Quantity-Numeral", "Quantity-Word",  "Modality (English) x Timing (Later)"), dv.labels = c("Reference group: Numeral-Word"), string.p = "p-value", string.est = "Estimate", string.se = "Standard Error", string.stat = "t-statistic")

tab_model(Map_58_I_ref, auto.label = FALSE, show.ci = FALSE, show.se = TRUE, show.stat = TRUE, show.est = TRUE, pred.labels = c("Intercept 1", "Intercept 2","Age", "SES", "Modality (English)", "Timing (Later)", "Large", "Numeral-Word", "Quantity-Numeral", "Modality (English) x Timing (Later)"), dv.labels = c("Reference group: Quantity-Word"), string.p = "p-value", string.est = "Estimate", string.se = "Standard Error", string.stat = "t-statistic")
```

* [Calculate model fit](https://www.stata.com/support/faqs/statistics/pseudo-r2/)
    + Log likelihood of null model: -455.3508
    + Log likelihood of our model: -336.7299
    + R-squared: 0.26
```{r}
summary(Map_58_null<- vglm(AvgCorr ~  1, tobit(Upper = 1.0), data = Map_58)) 
print(R2_Model2 <- 1 - (-336.7299 / -455.3508))
```

* Obtain mapping performance means for mapping pairs and set sizes
```{r}
QW_58 <- subset(Map_58, Map_58$MapPair == "Quantity-Word")
QN_58 <- subset(Map_58, Map_58$MapPair == "Quantity-Numeral")
NW_58 <- subset(Map_58, Map_58$MapPair == "Numeral-Word")
mean(QW_58$AvgCorr) 
mean(QN_58$AvgCorr) 
mean(NW_58$AvgCorr) 

Map_58_Med <- subset(Map_58, Map_58$SetSize == "Medium")
Map_58_Lrg <- subset(Map_58, Map_58$SetSize == "Large")
mean(Map_58_Med$AvgCorr) 
mean(Map_58_Lrg$AvgCorr) 
```

* Create subsetted dataframes for Timing and Modality (obtain ns and mean group performances)
    + Early: 64 children, M = 0.88
    + Later: 71 children, M = 0.80
    + English: 73 children, M = 0.85
    + ASL: 62 children, M = 0.82
```{r}
Early_58 <- (subset(Map_Inc_58, Map_Inc_58$Timing == "Early")) 
nrow(Early_58)
mean(Early_58$AvgCorrect_Total) 
Later_58 <- (subset(Map_Inc_58, Map_Inc_58$Timing == "Later")) 
nrow(Later_58) 
mean(Later_58$AvgCorrect_Total) 
English_58 <- (subset(Map_Inc_58, Map_Inc_58$Modality == "English")) 
nrow(English_58)
mean(English_58$AvgCorrect_Total) 
ASL_58 <- (subset(Map_Inc_58, Map_Inc_58$Modality == "ASL")) 
nrow(ASL_58) 
mean(ASL_58$AvgCorrect_Total) 
```

#### Explaining the Timing x Modality significant interaction
```{r  fig.align='center', fig.height=4, fig.width=9}
interaction.plot(Map_58$Timing, Map_58$Modality, Map_58$AvgCorr,  ylab = "Proportion Correct", xlab = "Language Timing", trace.label = "Language Modality", legend=TRUE, fixed=TRUE)
```
* Similar performances within Timing groups?   
    + Early: Yes (p = 0.84). ASL Early (M=0.89) & English Early (M=0.88)
    + Later: Yes (p=0.28). ASL Later (M=0.77) & English Later (M=0.83)
```{r}
wilcox.test(AvgCorrect_Total ~ Group_4cat, data = Early_58, exact = FALSE)
mean(subset(Early_58, Group_4cat == "ASL Early")$AvgCorrect_Total) 
mean(subset(Early_58, Group_4cat == "English Early")$AvgCorrect_Total)
```

```{r}
wilcox.test(AvgCorrect_Total ~ Group_4cat, data = Later_58, exact = FALSE)
mean(subset(Later_58, Group_4cat == "ASL Later")$AvgCorrect_Total)
mean(subset(Later_58, Group_4cat == "English Later")$AvgCorrect_Total) 
```



Perhaps children's age of language exposure within the Later group can explain the performance difference by modality (although not significant) within the Later group compared to the Early group. 

* Age of first language exposure demographics for Later groups
```{r message=FALSE, warning=FALSE, fig.align='center', fig.height=4, fig.width=5}
aggregate(Age.of.Exposure..mo..Language ~ Group_4cat, data=Later_58, mean)
aggregate(Age.of.Exposure..mo..Language ~ Group_4cat, data=Later_58, sd)
aggregate(Age.of.Exposure..mo..Language ~ Group_4cat, data=Later_58, range)
ggplot(data=Later_58, mapping = aes(x= Group_4cat, y=Age.of.Exposure..mo..Language)) + geom_boxplot() + geom_dotplot(alpha=0.7, dotsize = .8, method = "dotdensity", binaxis = "y", stackdir = "center") + theme_bw() + theme(legend.position="top", text = element_text(size=14), axis.title.x=element_blank(), panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + ylab("Age of first exposure to language (months)") 
```

* Does age of first language exposure differ between children exposed to language Later (e.g., ASL Later and English Later groups)?
    + Used Wilcoxon Sum Rank Test due to the data not being normally distributed (Shapiro-Wilk: p < 0.05)
    + Yes, ASL Later children are exposed to language significantly later than English Later children. W = 927, p < 0.001
```{r}
shapiro.test(Later_58$Age.of.Exposure..mo..Language)
wilcox.test(Later_58$Age.of.Exposure..mo..Language ~ Later_58$Group_4cat, exact = FALSE)

aggregate(Age.of.Exposure..mo..Language ~ Group_4cat, data=Later_58, mean)
aggregate(Age.of.Exposure..mo..Language ~ Group_4cat, data=Later_58, sd)
aggregate(Age.of.Exposure..mo..Language ~ Group_4cat, data=Later_58, range)
ggplot(data=Later_58, mapping = aes(x= Group_4cat, y=Age.of.Exposure..mo..Language)) + geom_boxplot() + geom_dotplot(alpha=0.7, dotsize = .8, method = "dotdensity", binaxis = "y", stackdir = "center") + theme_bw() + theme(legend.position="top", text = element_text(size=14), axis.title.x=element_blank(), panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + ylab("Age of first exposure to language (months)")
```


#### Linear Regression Model
```{r}
which(colnames(Map_Inc)=="Sum_Med_QW") #352
which(colnames(Map_Inc)=="Sum_Lrg_WN") #357
L_long <- pivot_longer(Map_Inc, cols = 352:357, values_to = "SumCorr")
which(colnames(L_long)=="Item1_QN_Answer") #35
which(colnames(L_long)=="Item51_WN_Correct.") #343
L_short <- L_long[,-c(35:343)]
L_short <-  mutate(L_short, SetSize = case_when(grepl("Med", L_short$name) ~"Medium", grepl("Lrg", L_short$name) ~"Large"))
L_short$SetSize <- as.factor(factor(as.character(L_short$SetSize), levels=c("Medium", "Large"), exclude=""))
L_short <- mutate(L_short, MapPair = case_when(grepl("QW", L_short$name) ~ "Quantity-Word", grepl("QN", L_short$name) ~"Quantity-Numeral", grepl("WN", L_short$name) ~"Numeral-Word"))
L_short$MapPair <- as.factor(factor(as.character(L_short$MapPair), levels=c("Numeral-Word","Quantity-Numeral", "Quantity-Word"), exclude=""))
L_short$MapPair_refQW <- as.factor(factor(as.character(L_short$MapPair), levels=c("Quantity-Word","Numeral-Word","Quantity-Numeral"), exclude=""))
```

View(L_short)

```{r}
#https://www.statmethods.net/stats/regression.html 
Map_lm <- lm(SumCorr ~ Age_Rounded + SES + Modality + Timing + SetSize + MapPair + Timing:Modality, data=L_short)
summary(Map_lm)
#Multiple R-squared:  0.2739,	Adjusted R-squared:  0.2688 
#F-statistic: 53.33 on 8 and 1131 DF,  p-value: < 2.2e-16

Map_lm_ref <- lm(SumCorr ~ Age_Rounded + SES + Modality + Timing + SetSize + MapPair_refQW + Timing:Modality, data=L_short)
summary(Map_lm_ref)

Map_lm_null <- lm(SumCorr ~ 1, data=L_short)

anova(Map_lm, Map_lm_null) #p < .001

#https://cran.rstudio.com/web/packages/olsrr/vignettes/residual_diagnostics.html
ols_plot_resid_qq(Map_lm)
ols_test_normality(Map_lm)
ols_plot_resid_hist(Map_lm)
ols_test_correlation(Map_lm)
ols_plot_resid_fit(Map_lm)
```


# OTHER CODES IN ANOTHER FILE... EDIT ONCE DECIDE TOBIT OR LINEAR! 

