---
title: "Mapping_AllGrps_OTHERCODES"
author: "Kristin Walker"
date: "3/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

> QUESTION 2: What other language-related variables predict children’s mapping skills?

* Does ASL expressive vocabulary knowledge differ between children exposed to language early and later (e.g., ASL Early and ASL Later groups)?
```{r}
nrow(ASL_58) #62 kids
shapiro.test(ASL_58$PN_PropCorr) #p < 0.006
wilcox.test(ASL_58$PN_PropCorr ~ ASL_58$Group_4cat, exact = FALSE) #W = 212.5, p-value = 0.02686

aggregate(PN_PropCorr ~ Group_4cat, data=ASL_58, mean) #M = 0.88 (SD = 0.07)
aggregate(PN_PropCorr ~ Group_4cat, data=ASL_58, sd) #M = 0.80 (SD = 0.12)


ggplot(data=ASL_58, mapping = aes(x= Group_4cat, y=PN_PropCorr)) + geom_boxplot() + geom_dotplot(alpha=0.7, dotsize = .8, method = "dotdensity", binaxis = "y", stackdir = "center") + theme_bw() + theme(legend.position="top", text = element_text(size=14), axis.title.x=element_blank(), panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + ylab("Picture Naming Proportion Correct") # REMOVED 27 ROWS, so only 35 kids
```

* Should have *__1170 entries / 9 = 130 children__*
        + missing 1 highest count b/c child refused to participate for that task
        + missing 4 age of first language exposure information
* Outcome variable: Overall Mapping Performance
* Final Model Predictors: Age + SES + Set Size + Map Pair + Age of first language exposure (AoLE), highest count, spontaneous counting
* Result: all significant

```{r}
Map_58_M <- subset(Map_58, Map_58$HC_Conservative != "N/A" & Map_58$Age.of.Exposure..mo..Language !="N/A")
nrow(Map_58_M) 
```

#### Tobit Model Comparisons
* Null 
    + Log likelihood of null model: -694.3
```{r results='hide'}
summary(Map_58_M_null<- vglm(AvgCorr ~  1, tobit(Upper = 1.0), data = Map_58_M)) 
```
* Base (Age, SES, Set Size, Map Pair)
```{r}
summary(Map_58_Base<- vglm(AvgCorr ~  Age_Rounded + SES + Set_Size + MapPair, tobit(Upper = 1), data = Map_58_M))
1-(-547.69/-694.3) 
```
* Base + Timing
```{r}
summary(Map_58_T<- vglm(AvgCorr ~  Age_Rounded + SES + Set_Size + MapPair + Timing, tobit(Upper = 1), data = Map_58_M))
1-(-536.9/-694.3)
```
* Base + AoLE
```{r}
summary(Map_58_AoLE<- vglm(AvgCorr ~  Age_Rounded + SES + Set_Size + MapPair + Age.of.Exposure..mo..Language, tobit(Upper = 1), data = Map_58_M))
1-(-530.63/-694.3) 
```
* Base + Timing + AoLE
```{r}
summary(Map_58_T_AoLE<- vglm(AvgCorr ~  Age_Rounded + SES + Set_Size + MapPair + Timing + Age.of.Exposure..mo..Language, tobit(Upper = 1), data = Map_58_M))
1-(-530.6/-694.3)
```
* Motivation for subsequent models  
    + Similar model fits for models with or without timing
    + AoLE appears to account for the variability in timing of language exposure
    + Therefore, we do not include Timing for the remaining models
* Base + AoLE + Highest Count
```{r}
summary(Map_58_AoLE_HC<- vglm(AvgCorr ~  Age_Rounded + SES + Set_Size + MapPair + Age.of.Exposure..mo..Language + HC_Conservative, tobit(Upper = 1), data = Map_58_M))
1-(-518.6464/-694.3) 
```
* BASE + AoLE + Highest Count + Spontaneous Counting
```{r}
summary(Map_58_AoLE_HC_SC<- vglm(AvgCorr ~  Age_Rounded + SES + Set_Size + MapPair + Age.of.Exposure..mo..Language + HC_Conservative + Prop_CountingBehavior_All, tobit(Upper = 1), data = Map_58_M))
1-(-499.804/-694.3) 
```

#### Final Tobit Model Table (NEED TO ADD R-SQUARED VALUES...)
```{r}
tab_model(Map_58_AoLE_HC_SC, auto.label = FALSE, show.ci = FALSE, show.se = TRUE, show.stat = TRUE, show.est = TRUE, pred.labels = c("Intercept 1", "Intercept 2","Age", "SES", "Medium", "Large", "Quantity-Numeral", "Quantity-Word", "Age of First Language Exposure", "Count Sequence", "Spontaneous Counting"), dv.labels = c("Final Tobit Model"), string.est = "Estimate", string.p = "p-value", string.se = "Standard Error", string.stat = "t-statistic") 
```

#### Tobit Model Comparison Table (NEED TO ADD R-SQUARED VALUES...)

```{r}
tab_model(Map_58_Base, Map_58_T, Map_58_AoLE, Map_58_T_AoLE, Map_58_AoLE_HC, auto.label = FALSE, show.ci = FALSE, show.se = TRUE, show.stat = TRUE, show.est = TRUE, pred.labels = c("Intercept 1", "Intercept 2","Age", "SES", "Medium", "Large", "Quantity-Numeral", "Quantity-Word", "Timing", "Age of First Language Exposure", "Count Sequence"), dv.labels = c("Base", "With Timing", "With Language Exposure", "With Timing and Language Exposure", "With Count Sequence"), string.est = "Estimate", string.p = "p-value", string.se = "Standard Error", string.stat = "t-statistic") 
```

#### Visualizations
* Create dataframe
    + Should still have 130 children
```{r}
Map_Inc_58_L <- subset(Map_Inc_58, Map_Inc_58$HC_Conservative != "N/A" & Map_Inc_58$Age.of.Exposure..mo..Language !="N/A")
nrow(Map_Inc_58_L) 
```

```{r results='hide'}
l <- ggplot(data = Map_Inc_58_L, mapping = aes(x=Age.of.Exposure..mo..Language, y=AvgCorrect_Total)) + geom_point() + geom_smooth(method="loess", color="black") + labs(x="Age of Language Exposure (months)", title = "a") + theme_bw() + theme(legend.position="top", text = element_text(size=16), axis.title.y=element_blank(), panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + coord_cartesian(xlim = c(0, 100), ylim= c(0.2,1)) + scale_y_continuous(breaks=c(0.2, 0.4, 0.6, 0.8, 1)) + scale_x_continuous(breaks=c(0, 25, 50, 75, 100))
s <- ggplot(data = Map_Inc_58_L, mapping = aes(x=Prop_CountingBehavior_All, y=AvgCorrect_Total)) + geom_point() + geom_smooth(method="loess", color="black") + labs(x="Proportion of Spontaneous Counting", title = "b") + theme_bw() + theme(legend.position="top", text = element_text(size=16), axis.title.y=element_blank(), panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + coord_cartesian(xlim = c(0, 1), ylim= c(0.2,1)) + scale_y_continuous(breaks=c(0.2, 0.4, 0.6, 0.8, 1)) + scale_x_continuous(breaks=c(0, 0.2, 0.4, 0.6, 0.8, 1))
h <- ggplot(data = Map_Inc_58_L, mapping = aes(x=HC_Conservative, y=AvgCorrect_Total)) + geom_point() + geom_smooth(method="loess", color="black") + labs(x="Count Sequence Knowledge", title = "c") + theme_bw() + theme(legend.position="top", text = element_text(size=16), panel.border = element_blank(), axis.title.y=element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + coord_cartesian(xlim = c(0, 100), ylim= c(0.2,1)) + scale_y_continuous(breaks=c(0.2, 0.4, 0.6, 0.8, 1)) + scale_x_continuous(breaks=c(0, 25, 50, 75, 100))
```

```{r message=FALSE, fig.align='center'}
grid.arrange(arrangeGrob(l,s,h, left = text_grob("Proportion Correct", rot = 90, vjust = 1, size = 16)))
```

#### Do children's ASL expressive vobabulary skills predict their mapping performance? 
* Outcome variable: Overall Mapping Performance
* Predictors: Picture Naming performance + Base
* Only have this measure for a subset of ASL children (n=62)
    + Should have 35 children (315 rows): 21 ASL Early and 14 ASL Later
```{r}
nrow(ASL_58)
ASL_58_PN <- subset(ASL_58, ASL_58$PN_PropCorr !="N/A")
nrow(ASL_58_PN)
sum(ASL_58_PN$Group_4cat == "ASL Early") 
sum(ASL_58_PN$Group_4cat == "ASL Later") 
```

```{r}
shapiro.test(ASL_58_PN$PN_PropCorr)
wilcox.test(PN_PropCorr ~ Group_4cat, data = Map_Inc_58, exact = FALSE)
mean(subset(ASL_58_PN, Group_4cat == "ASL Early")$PN_PropCorr) 
mean(subset(ASL_58_PN, Group_4cat == "ASL Later")$PN_PropCorr) 
```

#### TOBIT MODEL
```{r}
Map_58_ASL <- subset(Map_58, Map_58$Modality == "ASL" & Map_58$PN_PropCorr !="N/A")
nrow(Map_58_ASL)
```
* Null 
    + Log likelihood of null model: -164.6
```{r results='hide'}
summary(Map_58_PN_null<- vglm(AvgCorr ~  1, tobit(Upper = 1.0), data = Map_58_ASL)) 
```
* Only Picture Naming
    + Still not significant (no longer any error)
```{r}
summary(Map_58_PN<- vglm(AvgCorr ~  PN_PropCorr, tobit(Upper = 1.0), data = Map_58_ASL)) 
```
* Base (Age, SES, Set Size, Map Pair)
```{r}
summary(Map_58_PN_Base<- vglm(AvgCorr ~  Age_Rounded + SES + Set_Size + MapPair, tobit(Upper = 1), data = Map_58_ASL))
1-(-121.1/-164.6) 
```
* Base + Picture Naming
    + Convergence not obtained
```{r}
summary(Map_58_PN_T<- vglm(AvgCorr ~  Age_Rounded + SES + Set_Size + MapPair + PN_PropCorr, tobit(Upper = 1), data = Map_58_ASL))
1-(-120.8/-164.6)
```


> QUESTION 3: Does language timing and/or modality affect children’s performance on mapping pairs differently?

* Reorder Mapping Pairs to: QN, QW, NW
```{r results='hide'}
T_short$MapPair <- as.factor(factor(as.character(T_short$MapPair), levels=c("Quantity-Numeral", "Quantity-Word", "Numeral-Word"), exclude=""))
str(T_short$MapPair)
```
* 8 to 9-year-olds mapping pair performance
    + Should have 495 entries (n=55)
```{r fig.align='center', fig.height=4, fig.width=5}
Map_89 <- subset(T_short, T_short$Age_Rounded >=8)
nrow(Map_89) 
map_89 <- ggplot(Map_89, aes(MapPair, AvgCorr)) + geom_boxplot() + labs(x="Mapping Pairs", y="Proportion Correct") + scale_y_continuous (breaks=c(0.2, 0.4, 0.6, 0.8, 1.0), limits = c(0.2,1.0), expand = c(0,0)) + theme_bw() + theme(legend.position="top", text = element_text(size=16), axis.title.x=element_blank(), panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
map_89
```

#### Tobit models: Mapping Pairs
* Numeral-Word Tobit Model
    + CONVERGENCE NOT OBTAINED... HAVE TOO MANY PREDICTORS? DOES THIS MEAN NOT A GOOD MODEL?
    + Null log likelihood: -174.7
    + 78% of 4;6 - 7;11 year olds at ceiling 
```{r results='hide'}
summary(NW_58_null<- vglm(AvgCorr ~  1, tobit(Upper = 1.0), data = NW_58)) 
```

```{r}
summary(NW_58_I<- vglm(AvgCorr ~  Age_Rounded + SES + Modality + Timing + Set_Size + Modality:Timing, tobit(Upper = 1), data = NW_58))
print(R2_NW <- 1 - (-154.2  / -174.7))

Ceil_NW <- NW_58$AvgCorr
All_NW <- 1 #ceiling performance 
Var_NW <- length(which(Ceil_NW>= All_NW)) #number of observations equal to ceiling 
N_NW <- nrow(NW_58) #number of total observations
(Var_NW/N_NW)*100 
```

* Quantity-Word Tobit Model
    + Null log likelihood: -242.2
```{r results='hide'}
summary(QW_58_null<- vglm(AvgCorr ~  1, tobit(Upper = 1.0), data = QW_58)) 
```

```{r}
summary(QW_58_I<- vglm(AvgCorr ~  Age_Rounded + SES + Modality + Timing + Set_Size + Modality:Timing, tobit(Upper = 1), data = QW_58))
print(R2_QW <- 1 - (-186.5  / -242.2)) 
```
* Quantity-Numeral Tobit Model
    + Null log likelihood: 256.8
```{r results='hide'}
summary(QN_58_null<- vglm(AvgCorr ~  1, tobit(Upper = 1.0), data = QN_58))
```

```{r}
summary(QN_58_I<- vglm(AvgCorr ~  Age_Rounded + SES + Modality + Timing + Set_Size + Modality:Timing, tobit(Upper = 1), data = QN_58))
print(R2_QN <- 1 - (-188.3 / -256.8)) 
```

* Output table
OK TO INCLUDE NUMERAL-WORD?
```{r}
tab_model(QW_58_I, QN_58_I, NW_58_I, auto.label = FALSE, show.ci = FALSE, show.se = TRUE, show.stat = TRUE, show.est = TRUE, pred.labels = c("Intercept 1", "Intercept 2","Age", "SES", "Modality (English)", "Timing (Later)", "Medium", "Large", "Modality (English) x Timing (Later)"), dv.labels = c("Quantity-Word", "Quantity-Numeral", "Numeral-Word"), string.p = "p-value", string.est = "Estimate", string.se = "Standard Error", string.stat = "t-statistic")
```

* Reference Models + Output table
OK TO INCLUDE NUMERAL-WORD?
```{r results='hide'}
summary(QW_58_I_ref<- vglm(AvgCorr ~  Age_Rounded + SES + Modality + Timing + Set_Size_refM + Modality:Timing, tobit(Upper = 1), data = QW_58))
summary(QN_58_I_ref<- vglm(AvgCorr ~  Age_Rounded + SES + Modality + Timing + Set_Size_refM + Modality:Timing, tobit(Upper = 1), data = QN_58))
summary(NW_58_I_ref<- vglm(AvgCorr ~  Age_Rounded + SES + Modality + Timing + Set_Size_refM + Modality:Timing, tobit(Upper = 1), data = NW_58))
tab_model(QW_58_I_ref, QN_58_I_ref, NW_58_I_ref, auto.label = FALSE, show.ci = FALSE, show.se = TRUE, show.stat = TRUE, show.est = TRUE, pred.labels = c("Intercept 1", "Intercept 2","Age", "SES", "Modality (English)", "Timing (Later)", "Small", "Large", "Modality (English) x Timing (Later)"), dv.labels = c("Quantity-Word", "Quantity-Numeral", "Numeral-Word"), string.est = "Estimate", string.p = "p-value", string.se = "Standard Error", string.stat = "t-statistic")
```

* Mapping pair performance by timing and modality
```{r}
Early_QW_58 <- subset(QW_58, QW_58$Timing == "Early")
mean(Early_QW_58$AvgCorr) 
Later_QW_58 <- subset(QW_58, QW_58$Timing == "Later")
mean(Later_QW_58$AvgCorr) 
English_QW_58 <- subset(QW_58, QW_58$Modality == "English")
mean(English_QW_58$AvgCorr) 
ASL_QW_58 <- subset(QW_58, QW_58$Modality == "ASL")
mean(ASL_QW_58$AvgCorr) 
Early_QN_58 <- subset(QN_58, QN_58$Timing == "Early")
mean(Early_QN_58$AvgCorr) 
Later_QN_58 <- subset(QN_58, QN_58$Timing == "Later")
mean(Later_QN_58$AvgCorr) 
English_QN_58 <- subset(QN_58, QN_58$Modality == "English")
mean(English_QN_58$AvgCorr)
ASL_QN_58 <- subset(QN_58, QN_58$Modality == "ASL")
mean(ASL_QN_58$AvgCorr) 
```

```{r results='hide'}
Map_58$MapPair <- as.factor(factor(as.character(Map_58$MapPair), levels=c("Quantity-Numeral", "Quantity-Word", "Numeral-Word"), exclude=""))
nrow(Map_58)
modality_map <- ggplot(Map_58, aes(MapPair, AvgCorr, fill=Modality)) + geom_boxplot() + labs(x="Mapping Pairs", y="Proportion Correct", fill = "Modality") + ggtitle("a") + scale_y_continuous (breaks=c(0.2, 0.4, 0.6, 0.8, 1.0), limits = c(0.2,1.0), expand = c(0,0)) + theme_bw() + theme(legend.position="top", text = element_text(size=14), axis.title.x=element_blank(), panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+ scale_fill_manual(name = "Language Modality", breaks=c("ASL", "English"), values=c("tan2", "forestgreen"), labels=c("ASL (62)", "English (73)")) + scale_color_manual(name = "Language Modality", breaks=c("ASL", "English"), values=c("tan2", "forestgreen"), labels=c("ASL (62)", "English (73)"))  
timing_map <- ggplot(Map_58, aes(MapPair, AvgCorr, fill=Timing)) + geom_boxplot() + labs(x="Mapping Pairs", y="Proportion Correct", fill = "Timing") + ggtitle("b") + scale_y_continuous (breaks=c(0.2, 0.4, 0.6, 0.8, 1.0), limits = c(0.2,1.0), expand = c(0,0)) + theme_bw() + theme(legend.position="top", text = element_text(size=14), axis.title.x=element_blank(), panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + scale_fill_manual(name = "Language Timing", breaks=c("Early", "Later"), values=c("deepskyblue3", "firebrick3"), labels=c("Early (64)", "Later (71)")) + scale_color_manual(name = "Language Timing", breaks=c("Early", "Later"), values=c("deepskyblue3", "firebrick3"), labels=c("Early (64)", "Later (71)"))
```

```{r warning=FALSE, fig.align='center', fig.height=4, fig.width=10}
grid.arrange(modality_map,timing_map, nrow=1) 
```   

>  D/HH vs Hearing Mapping Performance

* Create Dataframe and add Hearing Status column
```{r}
Map_LDvH <- subset(Map_Inc_58, Map_Inc_58$Group_4cat == "English Early" | Map_Inc_58$Group_4cat == "English Later" | Map_Inc_58$Group_4cat == "ASL Later")
nrow(Map_LDvH) #ensure does not have ASL Early
Hearing_Status <- c()
for(i in 1:107)
Hearing_Status[i] <- ifelse(grepl("English Later", Map_LDvH$Group_4cat[i]), "Deaf", ifelse(grepl("ASL Later", Map_LDvH$Group_4cat[i]), "Deaf", "Hearing"))
Map_LDvH <- cbind(Map_LDvH, Hearing_Status)
sum(Map_LDvH$Hearing_Status == "Deaf") 
sum(Map_LDvH$Hearing_Status == "Hearing")
```

* Visualize D/HH vs Hearing mapping performance
```{r warning=FALSE, message=FALSE, fig.align='center', fig.height=4, fig.width=5}
LvH <- ggplot(data=Map_LDvH, mapping = aes(x= Hearing_Status, y=AvgCorrect_Total)) + geom_boxplot() + geom_dotplot(mapping=aes(fill=Hearing_Status, color=Hearing_Status), alpha=0.7, dotsize = .8, method = "dotdensity", binaxis = "y", stackdir = "center") + theme_bw() + theme(legend.position="top", text = element_text(size=14), axis.title.x=element_blank(), panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + ylab("Proportion Correct") + scale_fill_manual(name = "Hearing Status", breaks=c("Deaf", "Hearing"), values=c("grey0", "grey49"), labels=c("Deaf (96)", "Hearing (48)")) + scale_color_manual(name = "Hearing Status", breaks=c("Deaf", "Hearing"), values=c("grey0", "grey49"), labels=c("Deaf (96)", "Hearing (48)")) + stat_summary(fun=mean, geom="point", shape=18, size=5, color="black") + geom_hline(yintercept=0.25, linetype="dashed", color = "black")
LvH
```
* Do D/HH and Hearing children perform significantly differ on the mapping task?
    + Yes (p = 0.028). D/HH children (M = 0.90) perform signifcantly worse than hearing children (M = 0.94)
```{r}
Deaf_LvH <- subset(Map_LDvH, Map_LDvH$Hearing_Status == "Deaf")
Hearing_LvH <- subset(Map_LDvH, Map_LDvH$Hearing_Status == "Hearing")
median(Deaf_LvH$AvgCorrect_Total)
median(Hearing_LvH$AvgCorrect_Total) 
shapiro.test(Map_LDvH$AvgCorrect_Total) 
wilcox.test(Map_LDvH$AvgCorrect_Total ~ Map_LDvH$Hearing_Status, exact = FALSE)
```


>  Visualizing Four Group Mapping Performance

```{r warning=FALSE, message=FALSE, fig.align='center', fig.height=4, fig.width=10}
Map_Inc_58$Group_4cat <- as.factor(factor(as.character(Map_Inc_58$Group_4cat), levels=c("ASL Early", "English Early", "ASL Later", "English Later"), exclude=""))
nrow(Map_Inc_58)
Grps <- ggplot(data=Map_Inc_58, mapping = aes(x= Group_4cat, y=AvgCorrect_Total)) + geom_boxplot() + geom_dotplot(mapping=aes(fill=Group_4cat, color=Group_4cat), alpha=0.8, dotsize = .8, method = "dotdensity", binaxis = "y", stackdir = "center") + scale_y_continuous(breaks = c(0.2, 0.4, 0.6, 0.8, 1.0), limits = c(0.2,1.0)) + theme_bw() + theme(legend.position="top", text = element_text(size=14), axis.title.x=element_blank(), panel.border = element_blank(), panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black")) + ylab("Proportion Correct") + scale_fill_grey(name = "Groups", breaks=c("ASL Early", "English Early", "ASL Later", "English Later"), labels=c("ASL Early", "English Early", "ASL Later", "English Later")) + scale_color_grey(name = "Groups", breaks=c("ASL Early", "English Early", "ASL Later", "English Later"), labels=c("ASL Early", "English Early", "ASL Later", "English Later")) + stat_summary(fun=mean, geom="point", shape=18, size=5, color="black")
Grps
```


##WORK FOR CALLIE'S THESIS
```{r}
ID <- Total_Inc_Study$SUBJECT_ID
Any <- Total_Inc_Study$Prop_AnyCounting_All
Overt <- Total_Inc_Study$Prop_CountingBehavior_All
Point <- Total_Inc_Study$Prop_PointingBehavior_All
Map_Perf <- Total_Inc_Study$AvgCorrect_Total

Map_SponC <- data.frame(ID, Any, Overt, Point)
Map_SponC<- melt(Map_SponC, id.vars='ID')
names(Map_SponC)[names(Map_SponC) == "variable"] <- "Count_Type"
names(Map_SponC)[names(Map_SponC) == "value"] <- "Prop_Used"

Map_SponC2 <- data.frame(ID, Map_Perf)
Map_SponC3 <- merge(Map_SponC, Map_SponC2)
```
View(Map_SponC3)

```{r}
library("ggpubr")
ggboxplot(Map_SponC3, x = "Count_Type", y = "Map_Perf",
          ylab = "Mapping Performance (QN and QW)", xlab = "Spontaneous Counting Type")
```

```{r}
AnyCount <- subset(Map_SponC3, Map_SponC3$Count_Type == "Any")
OvertCount <- subset(Map_SponC3, Map_SponC3$Count_Type == "Overt")
PointCount <- subset(Map_SponC3, Map_SponC3$Count_Type == "Point")


#NEED TO CONFIRM WILCOXON BEST TO USE
wilcox.test(AnyCount$Prop_Used, AnyCount$Map_Perf, paired = TRUE, alternative = "two.sided")
wilcox.test(OvertCount$Prop_Used, OvertCount$Map_Perf, paired = TRUE, alternative = "two.sided")
wilcox.test(PointCount$Prop_Used, PointCount$Map_Perf, paired = TRUE, alternative = "two.sided")
```
View(AnyCount)


```{r}
Map_long1 <- pivot_longer(data = Total_Inc_Study, cols=c(ends_with("Answer")), names_to = c("Type"), values_to = "Quantity")
Map_long2 <- pivot_longer(data = Total_Inc_Study, cols=c(ends_with("Correct.")), names_to = c("Type2"), values_to = "Correct")
Map_long3 <- cbind(Map_long1, Map_long2)
Map_short <- Map_long3[,!grepl("^Item",names(Map_long3))] # delete columns that contain “item”

which(colnames(Map_short)=="SumTotal_QuantityNumeral") #34th column
which(colnames(Map_short)=="Sum_AnyCounting_All") #117th column
Map_short <- Map_short[, -c(34:117)] #removes unnecessary columns

# From Type column, create a new column (Map_Pair) for which IF Map_short$Type contains “NW” or “WN”, assign value “Numeral-Word” etc. 
Map_Pair <- c()
Map_short$Map_Pair <- ifelse(grepl("NW", Map_short$Type), "Numeral-Word", ifelse(grepl("WN", Map_short$Type), "Numeral-Word", ifelse(grepl("QN", Map_short$Type), "Quantity-Numeral", ifelse(grepl("NQ", Map_short$Type), "Quantity-Numeral", ifelse(grepl("QW", Map_short$Type), "Quantity-Word", ifelse(grepl("WQ", Map_short$Type), "Quantity-Word","bananas"))))))

#From Quantity column, create A new column (Set Size) for Medium (3-5) and Large (6-9) quntities 
Set_Size <- c()
Map_short$Set_Size <- case_when(Map_short$Quantity <3 ~ 'Small', Map_short$Quantity >= 3 & Map_short$Quantity<= 5 ~ 'Medium', Map_short$Quantity > 5 ~ 'Large')

#Remove rows for quantities 1 and 2 (practice trials) and Numeral-Word 
Map_short <- subset(Map_short, Quantity !=1 & Quantity !=2 & Map_Pair!="Numeral-Word")
```
View(Map_short)

```{r}
#HIGHLY SKEWED
d <- density(Map_short$Prop_CountingBehavior_All)
plot(d)

mean(Map_short$Prop_CountingBehavior_All)
range(Map_short$Prop_CountingBehavior_All)
```

```{r}
Bee <- ggplot(data=Total_Inc_Study, mapping = aes(x= Timing, y=Prop_CountingBehavior_All)) + geom_boxplot() + geom_dotplot(mapping=aes(fill=Modality, color=Modality), dotsize = 0.6, method = "dotdensity", binaxis = "y", stackdir = "center", alpha=0.8) + theme(legend.position="bottom", text = element_text(size=16), axis.title=element_text(size=16,face="bold"), legend.title=element_text(size=16), legend.text=element_text(size=16), axis.title.x=element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) + ylab("Spontaneous Counting Usage") + scale_x_discrete(labels=c("Early" = "Early Language", "Later" = "Later Language")) + scale_y_continuous(limits= c(0, 1.0), breaks= c(0, 0.2, 0.4, 0.6, 0.8, 1.0)) + scale_fill_manual(name = "Language Modality", values=c("slateblue4", "gold"), breaks=c("English", "ASL"), labels=c("English", "ASL")) + scale_color_manual(name = "Language Modality", values=c("slateblue4", "gold"), breaks=c("English", "ASL"), labels=c("English", "ASL")) 
Bee

ggscatter(data=Total_Inc_Study, x = "Age_Rounded", y = "Prop_CountingBehavior_All", 
          add = "reg.line", conf.int = TRUE, 
          xlab = "Age (years)", ylab = "Spontaneous Counting Usage")

ggscatter(data=Total_Inc_Study, x = "SES", y = "Prop_CountingBehavior_All", 
          add = "reg.line", conf.int = TRUE, 
          xlab = "SES", ylab = "Spontaneous Counting Usage")

ggboxplot(Total_Inc_Study, x = "Timing", y = "Prop_CountingBehavior_All", 
          color = "Timing", palette = c("#00AFBB", "#E7B800"),
          order = c("Early", "Later"),
          ylab = "Expressive Spontaneous Counting Usage", xlab = "Timing")

ggboxplot(Total_Inc_Study, x = "Modality", y = "Prop_CountingBehavior_All", 
          color = "Modality", palette = c("#00AFBB", "#E7B800"),
          order = c("ASL", "English"),
          ylab = "Expressive Spontaneous Counting Usage", xlab = "Modality")

ggviolin(Total_Inc_Study, x = "Timing", y = "Prop_CountingBehavior_All", 
          color = "Timing", palette = c("#00AFBB", "#E7B800"),
          order = c("Early", "Later"),
          ylab = "Expressive Spontaneous Counting Usage", xlab = "Timing")

ggviolin(Total_Inc_Study, x = "Modality", y = "Prop_CountingBehavior_All", 
          color = "Modality", palette = c("#00AFBB", "#E7B800"),
          order = c("ASL", "English"),
          ylab = "Expressive Spontaneous Counting Usage", xlab = "Modality")

mean(Total_Inc_Study$Prop_CountingBehavior_All)
dplyr::count(subset(Total_Inc_Study, Prop_CountingBehavior_All >0))

mean(Early$Prop_CountingBehavior_All)
mean(Later$Prop_CountingBehavior_All)

wilcox.test(Total_Inc_Study$Prop_CountingBehavior_All ~ Total_Inc_Study$Timing, paired = FALSE, alternative = "two.sided")
#W = 3445.5, p-value = 0.001785
median(Early$Prop_CountingBehavior_All)
median(Later$Prop_CountingBehavior_All)

wilcox.test(Total_Inc_Study$Prop_CountingBehavior_All ~ Total_Inc_Study$Modality, paired = FALSE, alternative = "two.sided")
#W = 4525, p-value = 0.9708
median(ASL$Prop_CountingBehavior_All)
median(English$Prop_CountingBehavior_All)
```

View(Total_Inc_Study)
View(Total_Inc_Study$Timing)
View(Total_Inc_Study$Prop_CountingBehavior_All)








#SCATTERPLOT BY AGE WITH LINEAR MODEL LINE FIT
```{r}
plot(Map_Inc$Age_Rounded, Map_Inc$AvgCorrect_Total, xlab = "Age (years)", ylab = "Mapping Overall Proportion Correct") + abline(lm(Map_Inc$AvgCorrect_Total ~ Map_Inc$Age_Rounded, data = Map_Inc), col = "blue")
```


